Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2020-07-02 area_agg_seq_tsas.tex
using the latest version of acmart.cls
improved the tex of title

\begin{document}
\title
[Finding Optimal Sequences for Area Aggregation] %short title
{Finding Optimal Sequences for Area Aggregation---\\
  \texorpdfstring
    {\Astar vs.\ Integer Linear Programming} %title of the paper
    {A* vs.\ Integer Linear Programming} %title of the pdf
}

@@

\author{Dongliang Peng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{0000-0001-6848-3545}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
  \country{Germany}
}
\email{www1.informatik.uni-wuerzburg.de/peng}

>>>>

\begin{document}
\title
[Finding Optimal Sequences for Area Aggregation] %short title
{Finding Optimal Sequences for Area Aggregation---\\
  \texorpdfstring
    {\Astar vs.\ Integer Linear Programming}%title of the paper
    {A* vs.\ Integer Linear Programming}%title of the pdf
}

@@

\author{Dongliang Peng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{0000-0001-6848-3545}
\affiliation{%
  \institution{GIS Technology, 
  	Delft University of Technology}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
  \country{The Netherlands}
}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
  \country{Germany}
}
\email{http://www.gdmc.nl/staff/}
